%% Short CV -- Andre Sevenius Nilsen
%% Auto-generated condensed version. Compile: pdflatex cv-short.tex && pdflatex cv-short.tex

\documentclass[10pt, a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1.8cm, top=2cm, bottom=2cm]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{ifthen}

\definecolor{accent}{HTML}{2d5986}
\definecolor{lightgray}{gray}{0.5}

\hypersetup{
  colorlinks = true,
  urlcolor   = accent,
  linkcolor  = accent,
  citecolor  = accent,
  pdfauthor  = {Andre Sevenius Nilsen},
  pdftitle   = {Short CV -- Andre Sevenius Nilsen},
}

\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}%
  [\vspace{-0.4em}\rule{\linewidth}{0.5pt}]
\titlespacing{\section}{0pt}{1.2em}{0.5em}

\newcommand{\cventry}[4]{%
  \noindent
  \begin{minipage}[t]{2.5cm}\small\color{lightgray}#1\end{minipage}%
  \hspace{0.4em}%
  \begin{minipage}[t]{\dimexpr\textwidth-2.9cm\relax}%
    \textbf{#2}%
    \ifthenelse{\equal{#3}{}}{}{\newline\textit{#3}}%
    \ifthenelse{\equal{#4}{}}{}{\newline\small #4}%
  \end{minipage}%
  \par\vspace{0.4em}%
}

\newcommand{\cvitem}[2]{%
  \noindent
  \begin{minipage}[t]{2.5cm}\small\color{lightgray}#1\end{minipage}%
  \hspace{0.4em}%
  \begin{minipage}[t]{\dimexpr\textwidth-2.9cm\relax}#2\end{minipage}%
  \par\vspace{0.3em}%
}

\begin{document}
\pagestyle{plain}

\begin{center}
  {\huge\bfseries Andr\'e Sevenius Nilsen, PhD}\\[0.4em]
  {\normalsize Scientist \textbullet{} Writer \textbullet{} Philosopher}\\[0.5em]
  {\small
    Oslo, Norway
    \quad\textbar\quad
    \href{mailto:sevenius.nilsen@gmail.com}{sevenius.nilsen@gmail.com}
    \quad\textbar\quad
    \href{https://djfarmor.github.io}{djfarmor.github.io}
    \quad\textbar\quad
    \href{https://scholar.google.com/citations?user=A1E5s7AAAAAJ\&hl=en}{Google Scholar}%
  }
\end{center}

\vspace{0.4em}

% ==========================================================
\section{Employment}

\cventry{2025--present}{Researcher}{Kongsberg Hospital (PI: M.D.\ G.\ Ernst)}%
  {Funding applications and data analysis; ketamine--TMS for depression; memory and awareness during propofol sedation.}

\cventry{2016--present}{Researcher / PhD Candidate}{University of Oslo, Brain Signalling Group (PI: Prof.\ J.\,F.\ Storm)}%
  {PhD defended March 2026. Study design, acquisition, analysis, and writing. Topics: anaesthesia, sleep, consciousness, psychedelics, thalamocortical modelling. Methods: TMS-EEG, ERP, anaesthesia, sleep deprivation, computational modelling.}

\cventry{2015--2016}{Researcher}{Innlandet Hospital Trust (PI: Assoc.\ Prof.\ T.\ Endestad)}%
  {Lead analyst and writer for MRI/fMRI trauma study.}

\cventry{2014--2016}{Researcher}{University of Oslo, Hedonic Pharmacology Lab (PI: PhD S.\ Leknes)}%
  {Design, analysis, and writing for morphine-fMRI craving/reward study and oxytocin--eyetracking study.}

\cventry{2012--2013}{Scientific Assistant}{University of Oslo (PI: PhD I.\ Blix)}%
  {fMRI/MRI acquisition and analysis; psychological trauma study.}

% ==========================================================
\section{Education}

\cventry{2026}{Ph.D., Medicine and Health Science}{University of Oslo}%
  {Thesis: \textit{Consciousness: When Is It Present And How Would We Know?}\\
   Supervisors: Prof.\ J.\,F.\ Storm, PhD B.\,E.\ Juel, Prof.\ R.\,J.\ Huster.}

\cventry{2014}{M.Sc., Cognitive Neuroscience}{University of Oslo}%
  {Thesis: \textit{Right Inferior Frontal Gyrus and Motor Response Inhibition: A Real-Time fMRI Neurofeedback Study.} Grade A.}

\cventry{2012}{B.Sc., Informatics, Language, Logic and Psychology}{University of Oslo}%
  {Thesis: \textit{The Link Between Numerical Time Estimates and Stored Temporal References.} Grade A.}

% ==========================================================
\section{Selected Publications}

\begin{enumerate}[leftmargin=2em, label={[\arabic*]}, itemsep=0.25em]

  \item Bajwa, I.\,J., \textbf{Nilsen, A.\,S.}, \ldots, Storm, J.\,F., \& Juel, B.\,E. (2025).
        A repeated awakening study exploring the capacity of complexity measures to capture dreaming during propofol sedation.
        \textit{Scientific Reports}, 15(1).

  \item Wong, W., \ldots, \textbf{Nilsen, A.\,S.}, \ldots, \& Tsuchiya, N. (2025).
        A dream EEG and mentation database.
        \textit{Nature Communications}, 16(1).

  \item \textbf{Sevenius Nilsen, A.}, Storm, J.\,F., \& Juel, B.\,E. (2024).
        Does Cognitive Load Affect Measures of Consciousness?
        \textit{Brain Sciences}, 14(9):919.
        \href{https://doi.org/10.3390/brainsci14090919}{doi:10.3390/brainsci14090919}

  \item \textbf{Sevenius Nilsen, A.}, Arena, A., \& Storm, J.\,F. (2024).
        Exploring effects of anesthesia on complexity, differentiation, and integrated information in rat EEG.
        \textit{Neuroscience of Consciousness}, 2024(1):niae021.
        \href{https://doi.org/10.1093/nc/niae021}{doi:10.1093/nc/niae021}

  \item \textbf{Sevenius Nilsen, A.}, Juel, B.\,E., Th\"urer, B., Aamodt, A., \& Storm, J.\,F. (2022).
        Are we really unconscious in `unconscious' states? Common assumptions revisited.
        \textit{Frontiers in Human Neuroscience}, 16:987051.
        \href{https://doi.org/10.3389/fnhum.2022.987051}{doi:10.3389/fnhum.2022.987051}

  \item \textbf{Sevenius Nilsen, A.}, Juel, B.\,E., \& Marshall, W. (2019).
        Evaluating Approximations and Heuristic Measures of Integrated Information.
        \textit{Entropy}, 21(5):525.
        \href{https://doi.org/10.3390/e21050525}{doi:10.3390/e21050525}

\end{enumerate}

\noindent\small Full publication list: \href{https://scholar.google.com/citations?user=A1E5s7AAAAAJ\&hl=en}{Google Scholar}\normalsize

% ==========================================================
\section{Selected Talks \& Presentations}

\cventry{2025}{Invited Talk}{Molecular Medicine Department, University of Oslo}{}
\cventry{2023}{Talk \& Panel Discussion}{Student Society for Psychedelic Science, University of Oslo}{}
\cventry{2021}{Abstract \& Talk}{ConsciousBrainConcepts Annual Workshop, Oslo}{}
\cventry{2019}{Abstract \& Poster}{Association for the Scientific Study of Consciousness (ASSC)}{}
\cventry{2018}{Abstract \& Poster}{Society for Neuroscience (SfN), San Diego, CA, USA}{}
\cventry{2015}{Abstract \& Poster}{Society for Neuroscience (SfN), Chicago, USA}{}

% ==========================================================
\section{Teaching \& Supervision}

\cventry{2021--2024}{PSY4318: Multidisciplinary Studies of Consciousness}{University of Oslo}%
  {Course coordinator, syllabus designer, and lecturer.}
\cventry{2018}{MBV-SP100: Advanced Neurobiology}{University of Oslo}{Intermittent lecturer.}
\cventry{2013--2014}{PSY1010: Research Methods and Statistics}{University of Oslo}{Seminar leader.}

\noindent\small Main supervisor: 6 MSc/BSc theses (2018--2024, UiO \& Universitat Oldenburg).
Co-supervisor: 3 MSc theses (2019--2020, UiO). Also supervised 6 short-term internship students.\normalsize

% ==========================================================
\section{Grants \& Stipends}

\cventry{2025}{Grant for $\sim$2 Post-Doctoral Positions}{Helse S\o r-\O st}%
  {\textasciitilde\$400k USD. Memory formation and awareness during propofol sedation.}
\cventry{2025}{NFFO Stipend --- Consciousness Science Textbook}{NFFO}%
  {\textasciitilde\$30k USD.}
\cventry{2013}{NFR Summer Stipend}{Norges Forskningsr\aa d}%
  {\textasciitilde\$2k USD.}

% ==========================================================
\section{Awards \& Honours}

\cventry{2025}{3rd Place --- Forsker Grand Prix (Local Final)}{Forsker Grand Prix / Forskningsdagene}{}

% ==========================================================
\section{Service \& Editorial}

\cvitem{Review Editor}{Frontiers in Neuroscience / Neuroprosthetics (2022--present)}
\cvitem{Lead Editor}{Special Issue on Altered States of Consciousness, Frontiers in Brain Health (2025--2026)}
\cvitem{Reviewer}{13 journals incl.\ \textit{Science}, \textit{Nature}, \textit{NeuroImage}, \textit{Human Brain Mapping}}
\cvitem{Organizer}{UiO LifeScience Conference (2021, 2022); ConsciousBrainConcepts Workshop (2021)}

% ==========================================================
\section{Software \& Repositories}

\cventry{}{\href{https://github.com/andresni/pyconscious}{PyConscious}}{Python package}%
  {EEG-based measures of consciousness. Used in multiple published studies.}
\cventry{}{\href{https://github.com/andresni/NYP}{NYP (NEST YAML Platform)}}{Python/YAML framework}%
  {Large-scale thalamocortical neural network simulation platform ($\sim$50{,}000-neuron model).}

% ==========================================================
\section{Skills}

\cvitem{Programming}{Python, Matlab, Bash, \LaTeX, E-Basic, Java, C++}
\cvitem{Methods}{EEG, fMRI, TMS, TMS-EEG, ERP, MRI, eyetracking, computational modelling}
\cvitem{Software}{FSL, NEST, Freesurfer, AFNI, Neuroscan, SPSS, E-prime, Linux}
\cvitem{Languages}{Norwegian (native), English (fluent)}

\end{document}
