%% Curriculum Vitae -- Andre Sevenius Nilsen
%% Full CV. Compile: pdflatex cv.tex && pdflatex cv.tex

\documentclass[11pt, a4paper]{article}

% ---------- Packages ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=2.2cm, top=2.5cm, bottom=2.5cm]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{ifthen}

% ---------- Colours ----------
\definecolor{accent}{HTML}{2d5986}
\definecolor{lightgray}{gray}{0.5}

% ---------- Hyperlinks ----------
\hypersetup{
  colorlinks = true,
  urlcolor   = accent,
  linkcolor  = accent,
  citecolor  = accent,
  pdfauthor  = {Andre Sevenius Nilsen},
  pdftitle   = {CV -- Andre Sevenius Nilsen},
}

% ---------- Section headings ----------
\titleformat{\section}
  {\large\bfseries\color{accent}}
  {}{0em}{}[\vspace{-0.4em}\rule{\linewidth}{0.5pt}]
\titlespacing{\section}{0pt}{1.4em}{0.6em}

\titleformat{\subsection}[runin]
  {\normalsize\bfseries}
  {}{0em}{}[.\quad]
\titlespacing{\subsection}{0pt}{0.8em}{0em}

% ---------- Entry macro ----------
\newcommand{\cventry}[4]{%
  \noindent
  \begin{minipage}[t]{2.7cm}%
    \small\color{lightgray}#1%
  \end{minipage}%
  \hspace{0.4em}%
  \begin{minipage}[t]{\dimexpr\textwidth-3.1cm\relax}%
    \textbf{#2}%
    \ifthenelse{\equal{#3}{}}{}{\newline\textit{#3}}%
    \ifthenelse{\equal{#4}{}}{}{\newline\small #4}%
  \end{minipage}%
  \par\vspace{0.45em}%
}

\newcommand{\cvitem}[2]{%
  \noindent
  \begin{minipage}[t]{2.7cm}%
    \small\color{lightgray}#1%
  \end{minipage}%
  \hspace{0.4em}%
  \begin{minipage}[t]{\dimexpr\textwidth-3.1cm\relax}%
    #2%
  \end{minipage}%
  \par\vspace{0.3em}%
}

% ==========================================================
\begin{document}
\pagestyle{plain}

% ---------- Header ----------
\begin{center}
  {\Huge\bfseries Andr\'e Sevenius Nilsen, PhD}\\[0.5em]
  {\large Scientist \textbullet{} Writer \textbullet{} Philosopher}\\[0.6em]
  Oslo, Norway
  \quad\textbar\quad
  \href{mailto:sevenius.nilsen@gmail.com}{sevenius.nilsen@gmail.com}
  \quad\textbar\quad
  \href{https://djfarmor.github.io}{djfarmor.github.io}\\[0.3em]
  \href{https://scholar.google.com/citations?user=A1E5s7AAAAAJ\&hl=en}{Google Scholar}
  \quad\textbar\quad
  \href{https://www.linkedin.com/in/andre-sevenius-nilsen-b70771190}{LinkedIn}
  \quad\textbar\quad
  \href{https://bsky.app/profile/turntwine.bsky.social}{Bluesky}
\end{center}

\vspace{0.5em}

% ==========================================================
\section{Research Interests}

Intelligence, consciousness, decision making, the integrated brain, psychology, AI,
political and social science, metaphysics, game theory, complexity science, ethics,
philosophy of science, physics, futurism, history, simulation and modelling.

% ==========================================================
\section{Education}

\cventry{2026}{Ph.D., Medicine and Health Science}{Institute of Basic Medical Sciences, University of Oslo}%
  {Thesis: \textit{Consciousness: When Is It Present And How Would We Know? Testing Measures and Assumptions for Detecting Consciousness Across States and Substrates.}\\
   Supervisors: Prof.\ J.\,F.\ Storm, PhD B.\,E.\ Juel, Prof.\ R.\,J.\ Huster.}

\cventry{2014}{M.Sc., Cognitive Neuroscience}{Institute of Psychology, University of Oslo}%
  {Thesis: \textit{Right Inferior Frontal Gyrus and Motor Response Inhibition: A Real-Time fMRI Neurofeedback Study.}\\
   Grade A. Supervisors: Prof.\ Tor Endestad \& PhD Dag Aln\ae s.}

\cventry{2012}{B.Sc., Informatics, Language, Logic and Psychology}{Institute of Informatics, University of Oslo}%
  {Thesis: \textit{The Link Between Numerical Time Estimates and Stored Temporal References.}\\
   Grade A. Supervisor: PhD Torleif Hallkjellsvik.}

% ==========================================================
\section{Employment}

\cventry{2025--present}{Researcher}{Kongsberg Hospital (PI: M.D.\ G.\ Ernst)}%
  {Responsible for funding applications and data analysis. Projects include a study on
   combined ketamine and TMS for depression, and memory formation and awareness during
   propofol sedation (UiO \& Kongsberg Hospital).}

\cventry{2016--present}{Researcher / PhD Candidate}{University of Oslo, Brain Signalling Group (PI: Prof.\ J.\,F.\ Storm)}%
  {PhD candidate from 2020 with supervisors B.\,E.\ Juel \& J.\,F.\ Storm. Thesis defence: March 2026.
   Responsible for all aspects of the scientific process --- study design, data acquisition,
   analysis, and writing. Projects span behavioural and pharmacological experiments and
   modelling/simulation of large-scale neural networks. Topics include anaesthesia, sleep,
   consciousness, psychedelics, and computational modelling of thalamocortical systems.
   Methods: TMS-EEG, ERP, anaesthesia administration, sleep deprivation, behavioural paradigms.}

\cventry{2016}{Researcher}{University of Oslo, Hedonic Pharmacology Lab (PI: Prof.\ S.\ Leknes)}%
  {Co-responsible for implementation and analysis; assisted in acquisition. Study on binocular
   rivalry, salience, and aggression using intranasal oxytocin, eyetracking, and behavioural paradigms.}

\cventry{2015--2016}{Researcher}{Innlandet Hospital Trust (PI: Assoc.\ Prof.\ T.\ Endestad)}%
  {Main responsible for MRI, fMRI, and resting-state fMRI analysis, interpretation, manuscript writing
   and submission. Psychological trauma study using MRI and fMRI.}

\cventry{2015--2016}{Scientific Technician}{University of Oslo (Assoc.\ Prof.\ R.\ Huster)}%
  {Assisting in design, scripting, and implementation of multimodal EEG-fMRI neurofeedback.
   Behavioural inhibition study using real-time fMRI and EEG.}

\cventry{2014--2016}{Researcher}{University of Oslo, Hedonic Pharmacology Lab (PI: PhD S.\ Leknes)}%
  {Consulting on design, scripting, acquisition, and analysis. Craving and reward study using
   morphine administration, fMRI, rs-fMRI, biometrics, and behavioural paradigms.}

\cventry{2014--2016}{Scientific Assistant}{NKVTS / University of Oslo (PI: PhD I.\ Blix)}%
  {Main responsible for analysis; co-responsible for acquisition, interpretation, manuscript,
   and submission. Psychological trauma study using MRI, fMRI, rs-fMRI, and psychometrics.}

\cventry{2014}{ERP-Technician}{Rikshospitalet (Oslo University Hospital), Prof.\ S.\ Andersson}%
  {Responsible for EEG acquisition and ERP analysis for diagnostic purposes.}

\cventry{2014}{Researcher}{SafeeCom AS (PI: Dr.\ B.\,C.\ \O stberg)}%
  {Main responsible for prototyping of medical technologies: medical UWB radar scanner
   and vibrational diagnostic tool using Matlab and Arduino.}

\cventry{2012--2013}{Scientific Assistant}{University of Oslo (PI: PhD I.\ Blix)}%
  {Co-responsible for fMRI/MRI acquisition including recent traffic accident survivors.
   Psychological trauma study using MRI, fMRI, rs-fMRI, psychometrics, and behavioural paradigms.}

\cventry{2012--2013}{Lab Manager}{Cognitive Laboratories, University of Oslo (Assoc.\ Prof.\ T.\ Endestad)}%
  {Responsible for data acquisition, student lab days, analysis, booking, and IT communication.}

% ==========================================================
\section{Publications}

\subsection*{Journal Articles}

\begin{enumerate}[leftmargin=2em, label={[\arabic*]}, itemsep=0.4em]

  \item Bajwa, I.\,J., \textbf{Nilsen, A.\,S.}, \ldots, Storm, J.\,F., \& Juel, B.\,E. (2025).
        A repeated awakening study exploring the capacity of complexity measures to capture
        dreaming during propofol sedation.
        \textit{Scientific Reports}, 15(1).

  \item Wong, W., \ldots, \textbf{Nilsen, A.\,S.}, \ldots, \& Tsuchiya, N. (2025).
        A dream EEG and mentation database.
        \textit{Nature Communications}, 16(1).

  \item \textbf{Sevenius Nilsen, A.}, Storm, J.\,F., \& Juel, B.\,E. (2024).
        Does Cognitive Load Affect Measures of Consciousness?
        \textit{Brain Sciences}, 14(9):919.
        \href{https://doi.org/10.3390/brainsci14090919}{doi:10.3390/brainsci14090919}

  \item \textbf{Sevenius Nilsen, A.}, Arena, A., \& Storm, J.\,F. (2024).
        Exploring effects of anesthesia on complexity, differentiation, and integrated
        information in rat EEG.
        \textit{Neuroscience of Consciousness}, 2024(1):niae021.
        \href{https://doi.org/10.1093/nc/niae021}{doi:10.1093/nc/niae021}

  \item Aamodt, A., \textbf{Sevenius Nilsen, A.}, Markhus, R., Kusztor, A.,
        HasanzadehMoghadam, F., Kauppi, N., Th\"urer, B., Storm, J.\,F., \& Juel, B.\,E. (2023).
        EEG Lempel-Ziv complexity varies with sleep stage, but does not seem to track
        dream experience.
        \textit{Frontiers in Human Neuroscience}, 16:987714.
        \href{https://doi.org/10.3389/fnhum.2022.987714}{doi:10.3389/fnhum.2022.987714}

  \item \textbf{Sevenius Nilsen, A.}, Juel, B.\,E., Th\"urer, B., Aamodt, A., \& Storm, J.\,F. (2022).
        Are we really unconscious in `unconscious' states? Common assumptions revisited.
        \textit{Frontiers in Human Neuroscience}, 16:987051.
        \href{https://doi.org/10.3389/fnhum.2022.987051}{doi:10.3389/fnhum.2022.987051}

  \item \textbf{Nilsen, A.\,S.}, Juel, B.\,E., Farnes, N., Romundstad, L., \& Storm, J.\,F. (2021).
        Behavioral effects of sub-anesthetic ketamine in a go/no-go task.
        \textit{Journal of Psychedelic Studies}, 4(3), 156--162.

  \item Halder, S., Juel, B.\,E., \textbf{Sevenius Nilsen, A.}, Raghavan, L.\,V., \& Storm, J.\,F. (2021).
        Changes in measures of consciousness during anaesthesia of one hemisphere (Wada test).
        \textit{NeuroImage}, 226:117566.
        \href{https://doi.org/10.1016/j.neuroimage.2020.117566}{doi:10.1016/j.neuroimage.2020.117566}

  \item Aamodt, A., \textbf{Sevenius Nilsen, A.}, Th\"urer, B., HasanzadehMoghadam, F.,
        Kauppi, N., Juel, B.\,E., \& Storm, J.\,F. (2021).
        EEG Signal Diversity Varies With Sleep Stage and Aspects of Dream Experience.
        \textit{Frontiers in Psychology}, 12:655884.
        \href{https://doi.org/10.3389/fpsyg.2021.655884}{doi:10.3389/fpsyg.2021.655884}

  \item Farnes, N., Juel, B.\,E., \textbf{Nilsen, A.\,S.}, Romundstad, L.\,G., \& Storm, J.\,F. (2020).
        Increased signal diversity/complexity of spontaneous EEG, but not evoked EEG responses,
        in ketamine-induced psychedelic state in humans.
        \textit{PLOS ONE}, 15(11), e0242056.

  \item Kusztor, A., Raud, L., Juel, B.\,E., \textbf{Nilsen, A.\,S.}, Storm, J.\,F., \& Huster, R.\,J. (2019).
        Sleep deprivation differentially affects subcomponents of cognitive control.
        \textit{Sleep}, 42(4), zsz016.

  \item \textbf{Sevenius Nilsen, A.}, Juel, B.\,E., \& Marshall, W. (2019).
        Evaluating Approximations and Heuristic Measures of Integrated Information.
        \textit{Entropy}, 21(5):525.
        \href{https://doi.org/10.3390/e21050525}{doi:10.3390/e21050525}

  \item Wortinger, L.\,A., Endestad, T., Melinder, A.\,M.\,D., \O ie, M.\,G.,
        \textbf{Nilsen, A.\,S.}, \& Wyller, V.\,B. (2016).
        Aberrant resting-state functional connectivity in the salience network of adolescent
        chronic fatigue syndrome.
        \textit{PLOS ONE}, 11(7), e0159351.

  \item \textbf{Nilsen, A.\,S.}, Blix, I., Leknes, S., Ekeberg, \O ., Skogstad, L.,
        Endestad, T., \& Heir, T. (2016).
        Brain activity in response to trauma-specific, negative, and neutral stimuli:
        A fMRI study of recent road traffic accident survivors.
        \textit{Frontiers in Psychology}, 7, 1173.

  \item \textbf{Nilsen, A.\,S.}, Hilland, E., Kogstad, N., Heir, T., Hauff, E., Lien, L.,
        \& Endestad, T. (2016).
        Right temporal cortical hypertrophy in resilience to trauma: an MRI study.
        \textit{European Journal of Psychotraumatology}, 7.
        \href{http://doi.org/10.3402/ejpt.v7.31314}{doi:10.3402/ejpt.v7.31314}

\end{enumerate}

\subsection*{Preprints \& Working Papers}

\begin{enumerate}[leftmargin=2em, label={[\arabic*]}, itemsep=0.4em]

  \item \textbf{Sevenius Nilsen, A.} (2026).
        Newcomb's Paradox Under Epistemic Uncertainty: A Two-Stage Policy Analysis.
        \textit{PhilArchive}.

  \item \textbf{Nilsen, A.\,S.}, Juel, B.\,E., Th\"urer, B., \& Storm, J.\,F. (2020).
        Proposed EEG measures of consciousness: a systematic, comparative review.
        \textit{PsyArXiv}.

\end{enumerate}

\subsection*{Theses}

\begin{enumerate}[leftmargin=2em, label={[\arabic*]}, itemsep=0.4em]

  \item \textbf{Sevenius Nilsen, A.} (2026).
        \textit{Consciousness: When Is It Present And How Would We Know?
        Testing Measures and Assumptions for Detecting Consciousness Across States and Substrates.}
        PhD Thesis, University of Oslo.

  \item \textbf{Nilsen, A.\,S.} (2014).
        \textit{Right Inferior Frontal Gyrus and Motor Response Inhibition:
        A Real-Time fMRI Neurofeedback Study.}
        MSc Thesis, University of Oslo.
        \href{http://hdl.handle.net/10852/39807}{hdl.handle.net/10852/39807}

\end{enumerate}

\subsection*{Popular Science}

\begin{enumerate}[leftmargin=2em, label={[\arabic*]}, itemsep=0.4em]
  \item \textbf{Sevenius Nilsen, A.} (2021). Popular science article. \textit{MedisinBloggen}.
  \item \textbf{Sevenius Nilsen, A.} (2012--2014). Three popular science articles.
        \textit{Speilvendt}, student journal of psychology, University of Oslo.
\end{enumerate}

% ==========================================================
\section{Talks \& Presentations}

\cventry{2025}{Invited Talk}{Molecular Medicine Department, University of Oslo, Oslo}{}
\cventry{2023}{Talk \& Panel Discussion}{Student Society for Psychedelic Science, University of Oslo, Oslo}{}
\cventry{2023}{Talk}{Molecular Medicine Department, University of Oslo, Oslo}{}
\cventry{2021}{Abstract \& Talk}{ConsciousBrainConcepts Annual Workshop, Oslo}{}
\cventry{2021}{Abstract \& Talk}{Nordic Graduate Conference on the Philosophy of Mind}{}
\cventry{2019}{Abstract \& Poster}{Association for the Scientific Study of Consciousness (ASSC)}{}
\cventry{2018}{Abstract \& Poster}{Society for Neuroscience (SfN), San Diego, CA, USA}{}
\cventry{2018}{Abstract \& Poster}{Federation of European Neuroscience Societies (FENS), Berlin, Germany}{}
\cventry{2018}{Abstract \& Poster}{Association for the Scientific Study of Consciousness (ASSC), Krakow, Poland}{}
\cventry{2018}{Abstract \& Poster}{HBP-IC 1st --- Understanding Consciousness}{}
\cventry{2017}{Abstract, Poster \& Talk}{Human Brain Project 1st Student Conference}{}
\cventry{2017}{Abstract \& Poster}{Nordic Neuroscience Meeting}{}
\cventry{2017}{Abstract \& Poster}{Society for Neuroscience (SfN), Washington D.C., USA}{}
\cventry{2016}{Abstract \& Poster}{Reading Emotions, University of Reading, UK}{}
\cventry{2015}{Abstract \& Poster}{Society for Neuroscience (SfN), Chicago, USA}{}

% ==========================================================
\section{Teaching \& Supervision}

\subsection*{Teaching}

\cventry{2021--2024}{PSY4318: Multidisciplinary Studies of Consciousness}{University of Oslo}%
  {Course coordinator, syllabus designer, and lecturer.}

\cventry{2018}{MBV-SP100: Advanced Neurobiology}{University of Oslo}%
  {Intermittent lecturer.}

\cventry{2013--2014}{PSY1010: Research Methods and Statistics}{University of Oslo}%
  {Seminar leader.}

\subsection*{Supervision (Main Supervisor)}

\cventry{2024}{MSc, Neuroscience}{Universitat Oldenburg}%
  {Sub-anaesthetic ketamine for depression --- predictive factors.}
\cventry{2022}{MSc, Cognitive Neuroscience}{University of Oslo}%
  {Neurodynamic and experiential effects of sub-anaesthetic ketamine.}
\cventry{2022}{BSc, Neuroscience}{Universitat Oldenburg}%
  {Repeated masking and recurrent processing theory of consciousness.}
\cventry{2020}{MSc, Informatics}{University of Oslo}%
  {Evolutionary dynamics implemented in a neuromorphic computer.}
\cventry{2019}{MSc, Psychology}{University of Oslo}%
  {Gambling and addiction --- an exploration of the effect of personality on gambling.}
\cventry{2018}{MSc, Cognitive Neuroscience}{University of Oslo}%
  {Semantic and motoric inhibition --- same in kind or different in mind.}

\subsection*{Supervision (Co-Supervisor)}

\cventry{2020}{MSc, Cognitive Neuroscience}{University of Oslo}%
  {Validation of measures of consciousness during propofol anaesthesia.}
\cventry{2019}{MSc, Cognitive Neuroscience}{University of Oslo}%
  {Sub-anaesthetic ketamine and EEG-based measures of consciousness.}
\cventry{2019}{MSc, Cognitive Neuroscience}{University of Oslo}%
  {Sleep deprivation effect on motoric inhibition.}

\noindent\small Also supervised 6 students in short-term internship projects.\normalsize

% ==========================================================
\section{Grants \& Stipends}

\cventry{2025}{Grant for $\sim$2 Post-Doctoral Positions}{Helse S\o r-\O st}%
  {\textasciitilde\$400k USD. Responsible for writing the application.
   Project: memory formation and awareness during propofol sedation (UiO \& Kongsberg Hospital).}

\cventry{2025}{NFFO Stipend --- Consciousness Science Textbook}%
  {Norsk faglitter\ae r forfatter- og oversetterforening (NFFO)}%
  {\textasciitilde\$30k USD. Stipend for writing an introductory textbook on consciousness science.}

\cventry{2013}{NFR Summer Stipend (Master Thesis)}{Norges Forskningsr\aa d (NFR)}%
  {\textasciitilde\$2k USD. Main recipient of the Research Council of Norway's summer stipend.}

\cventry{2016--}{Co-applicant on Multiple Successful Grants}{Various (with B.\,E.\ Juel \& J.\,F.\ Storm)}%
  {Co-applicant on several successful grant applications supporting consciousness research at UiO.}

% ==========================================================
\section{Awards \& Honours}

\cventry{2025}{3rd Place --- Forsker Grand Prix (Local Final)}{Forsker Grand Prix / Forskningsdagene}%
  {3rd place in the local final of Norway's national science communication competition.}

% ==========================================================
\section{Service \& Editorial}

\cvitem{Review Editor}{Frontiers in Neuroscience / Neuroprosthetics (2022--present)}
\cvitem{Guest Assoc.\ Editor}{Frontiers in Brain Health and Clinical Neuroscience (2022--present)}
\cvitem{Lead Editor}{Special Issue: \textit{``Comparing Altered States of Consciousness:
  Phenomenology, Physiology, and Neural Mechanisms''}, Frontiers in Brain Health and Clinical Neuroscience (2025--2026)}

\medskip\noindent
\textbf{Ad hoc reviewer:} \textit{Science}; \textit{Nature}; \textit{Communications Biology};
\textit{Human Brain Mapping}; \textit{NeuroImage}; \textit{Clinical EEG and Neuroscience};
\textit{Frontiers in Neuroscience}; \textit{Frontiers in Integrative Neuroscience};
\textit{Frontiers in Neurology}; \textit{Journal of Psychedelic Studies};
\textit{European Child \& Adolescent Psychiatry}; \textit{Cellular Physiology and Biochemistry};
\textit{Social Cognitive and Affective Neuroscience}.

\medskip
\cvitem{Organizer}{UiO LifeScience Conference (2021, 2022)}
\cvitem{Organizer}{ConsciousBrainConcepts Workshop on Consciousness (2021)}
\cvitem{Examiner}{External examiner, MSc Cognitive Neuroscience, UiO (2016); Oral examiner $\times$7 (2018, 2021--2025)}
\cvitem{Section Rep.}{Section Representative for Temporarily Employed, UiO (2019--2021)}

% ==========================================================
\section{Software \& Repositories}

\cventry{}{\href{https://github.com/andresni/pyconscious}{PyConscious}}{Python package}{%
  EEG-based measures of consciousness (Lempel-Ziv complexity, permutation entropy,
  integrated information proxies, and more). Used in multiple published studies.}

\cventry{}{\href{https://github.com/andresni/NYP}{NYP (NEST YAML Platform)}}{Python/YAML framework}{%
  Parametrising and running large-scale thalamocortical neural network simulations in NEST.
  $\sim$50{,}000-neuron model of thalamocortical dynamics.}

% ==========================================================
\section{Skills}

\cvitem{Programming}{Python, Matlab, Bash, \LaTeX, E-Basic, Java, C++, Perl, VB}
\cvitem{Methods}{EEG, fMRI, rs-fMRI, rt-fMRI, MRI, TMS, TMS-EEG, ERP, eyetracking,
  pupillometry, psychometrics, computational modelling \& simulation}
\cvitem{Software}{FSL, Matlab, NEST, E-prime, Freesurfer, Linux, SPSS, AFNI, Neuroscan}
\cvitem{Languages}{Norwegian (native), English (fluent)}

\subsection*{Additional Courses}

\cvitem{2024}{Medical History (HES9320), UiO;
  Introduction to Statistics (MF9130), UiO}
\cvitem{2022}{Introduction to Machine Learning (IN4050), UiO;
  Neuroscience School of Advanced Studies (NSAS)}
\cvitem{2020}{Sprint School in Computational Neuroscience, EITN}
\cvitem{2019}{Multi-Agent Systems (TEK9010), UiO}
\cvitem{2017}{Computational Neuroscience (FYS488), NMBU}
\cvitem{Various}{Courses in philosophy, psychology, informatics, statistics, methods,
  and cognitive neuroscience (UiO)}

% ==========================================================
\section{Other}

\cvitem{Private tutoring}{Research methods and statistics (2014--2015)}
\cvitem{Popular science}{1 article in \textit{MedisinBloggen} (2021);
  3 articles in \textit{Speilvendt} (2012--2014)}

\end{document}
